Online Multiclass Linear Classification with Bandit Feedback

### 2018-11-13 arxiv-version/main.tex
Add definition of linear separability

% Math commands
\newcommand{\indicator}[1]{\mathbf{1}\left[#1 \right]}

@@

@@

\section{Algorithm for strongly linearly separable data}

>>>>

% Math environments
\newtheorem{definition}{Definition}
\newtheorem{proposition}[definition]{Proposition}
\newtheorem{lemma}[definition]{Lemma}
\newtheorem{theorem}[definition]{Theorem}
\newtheorem{corollary}[definition]{Corollary}

% Math symbols and commands
\newcommand{\R}{\mathbb{R}}  % set of real numbers
\newcommand{\indicator}[1]{\mathbf{1}\left[#1 \right]} % indicator
\newcommand{\ip}[2]{\left\langle #1, #2 \right\rangle} % inner product
\newcommand{\norm}[1]{\left\| #1 \right\|}  % norm of a vector or a matrix

@@

We define two notions of linear separability for multiclass classification. The
first notion is the standard notion of linear separability used in the proof of
mistake bound for the \textsc{Multiclass Perceptron} algorithm. The second
notion is stronger, i.e. more restrictive. However, it is more suitable for the
bandit setting, since it allows for a simple and efficient algorithm; see
Section~\ref{section:algorithm-for-strongly-linearly-separable-data}.

\begin{definition}
Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, let $K$ be a positive
integer, and let $\gamma$ be a positive real number. Let $(x_1, y_1), (x_2,
y_2), \dots, (x_T, y_T)$ labeled examples in $V \times \{1,2,\dots,K\}$.

The examples are said to be \emph{linearly separable with a
margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
that
\begin{align}
\label{equation:linear-separability-1}
& \sum_{i=1}^K \norm{w_i}^2 = 1 \; , \\
\label{equation:linear-separability-2}
& \forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \qquad \qquad \ip{x_t}{w_{y_t}} \ge \ip{x_t}{w_i} + \gamma \; .
\end{align}

The examples are said to be \emph{strongly linearly separable with a
margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
that
\begin{align}
\label{equation:strong-linear-separability-1}
\forall i \in \{1,2,\dots,K\} \qquad \qquad \norm{w_i}^2 & = 1 \; , \\
\label{equation:strong-linear-separability-2}
\forall t \in \{1,2,\dots,T\} \qquad \qquad \ip{x_t}{w_{y_t}} &\ge \gamma \; , \\
\label{equation:strong-linear-separability-3}
\forall t \in \{1,2,\dots,T\} \qquad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \qquad \qquad \ip{x_t}{w_i} & \le - \gamma \; .
\end{align}
\end{definition}

It is easy to see that if labeled examples are strongly linearly
separable with margin $\gamma$ then they are linearly separable with margin
$2\gamma/\sqrt{K}$. Indeed, if $w_1, w_2, \dots, w_K \in V$
satisfy \eqref{equation:strong-linear-separability-1},
\eqref{equation:strong-linear-separability-2},
\eqref{equation:strong-linear-separability-3} then $w_1' = w_1/\sqrt{K}, w_2' =
w_2/\sqrt{K}, \dots, w_K' = w_K/\sqrt{K}$ satisfy
\eqref{equation:linear-separability-1} and
\eqref{equation:linear-separability-2} with margin $\gamma' = 2\gamma/\sqrt{K}$.

Similarly, if $K=2$ and labeled examples are linearly separable
with a margin $\gamma$ then they are strongly linear separable with margin $??$.
Indeed, if $w_1, w_2$ satisfy \eqref{equation:linear-separability-1}
and \eqref{equation:linear-separability-2} then \dots

@@

\section{Algorithm for strongly linearly separable data}
\label{section:algorithm-for-strongly-linearly-separable-data}
